---
title: 'Semantic Priming: K. R.'
author: "Michael Espero"
date: "2/11/2018"
output:
  html_document: default
  pdf_document: default
---

```{r, echo=FALSE, results=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
knitr::opts_chunk$set(error = TRUE, cache = FALSE, comment = NA, tidy = TRUE)
```

## Introduction

This is a demonstration regarding semantic priming. For problems or suggestions, please contact me <michael.espero@cgu.edu>.

## Setup & Data Import
```{r Setup & Data Import, comment=NA, message=F, warning=F}
set.seed(789)

# This build only requires that you have the "easypackages" library pre-installed. If it throws an error, try installing "easypackages" with install.packages()
require(easypackages)
packages(
  "tidyverse", "broom", "skimr", "plotly", "apaTables", "GGally",
  "caret", "psych", "haven", "car", "ggthemes"
)

# We can make a pointer called "dat" to data we stored on Github.
dat <- "https://raw.githubusercontent.com/michaelespero/data-projects/master/dat_ex_1_semantic_priming.csv"

dat <- read_csv(dat) # Read in the data from the specified url.


# dat <- read_sav("eprime/exp_1_spss_data.sav")
# We can make a pointer called "dat" to data we stored on Github.
# Here, we filter the observations so only correct responses will be in dat.
dat <- dat %>%
  filter(TargetAcc == 1)

# Let's make sure we have only the correct responses.
# dat %>%
#  filter(TargetAcc == 1) %>%
#  count()

# We want Target Accuracy and Trial Type to work as factors
dat$TargetAcc <- as.factor(dat$TargetAcc)
dat$TrialType <- as.factor((dat$TrialType))

# Let's make it clear that our first column contains the number of each trial.
#names(dat)[names(dat) == "X1"] <- "TrialNum"

class(dat) # Is it a data frame?

dim(dat) # How many dimensions does our data have in terms of rows and columns?

skim(dat) # Now let's call up descriptive statistics and histograms.

# Is the dependent variable normally distributed?
skew(dat$TargetRT)
kurtosi(dat$TargetRT)
```

## Show

What do you notice?:

```{r show, echo=T, comment=NA, message=F, warning=F}
glimpse(dat)
# We can use this nifty function to make a matrix illustrating bivariate relationships in the data.
ggpairs(dat)

# 3D plots may be helpful in further exploration of how the data hangs together.

#p0 <- plot_ly(data = dat, z = ~TargetRT, x = ~TrialType, y = ~TargetAcc, opacity = 0.6) %>% add_markers(color = ~TargetAcc)
#p0
```

## Analyses

How might we test the data?:

```{r Analyze, echo=T, comment=NA, message=F, warning=F}

# Assumption Check: is the variance equal?
leveneTest(dat$TargetRT, group = dat$TrialType, center = mean)

# Specify the linear model
react_mod <- lm(TargetRT ~ TrialType, dat)

# Let's get some ANOVA output
kable(sjstats::anova_stats(react_mod), booktabs = T)

# Let's have another look with robust standard errors
Anova(
  react_mod, Type = "II",
  white.adjust = TRUE
)

# One more ANOVA, this time using the Welch's correction for unequal variance.
oneway.test(
  TargetRT ~ TrialType,
  data = dat,
  var.equal = FALSE
)

# How do the means line up by trial type?
TukeyHSD(aov(react_mod))

plot(TukeyHSD(aov(TargetRT ~ TrialType, dat)))
```

## Interpretation

It appears that regardless of trial type (nonword, unrelated word, related word), K. R. remained consistent with regards to speed of response and accuracy. For K. R., there appears to be no semantic priming effect in the sample at hand.